\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-05-17 redaction/dhp_sept2016.tex
chnagement encore

\todo{expliciter ici notre strategie d'estimation par rapport a Hummels et Skiba, 2004. In the terms of \cite{hummels_skiba}, our estimation strategy allows for a varying $\beta$ across time, country partner and product.}

@@

If we share this view with \citet{hummels2007}, our strategy for eliminating composition effects differs from his in two main respects. First, we provide a broader characterization of the time trends in transport costs as our empirical analysis allows for a more flexible estimation of the share between the additive and the ad-valorem components of transport costs. In characterizing the time trend in the ``pure transport costs'', \citet{hummels2007} eliminates the changes in the price per kilo dimension, attributing this to a change in the composition of the bundle over time (per country-commodity).\footnote{See \citet{hummels2007}, p. 146.} By contrast, our estimation strategy allows for an explicit decomposition of the additive cost component over time/product/country partner. \textbf{stop here} By comparing the additive cost component unfitted (total) and fitted (composition effects excluded), we are thus able to characterize if this dimension of the transport cost has fallen due to (for instance) the fact that product quality has increased over time (weight has reduced, hence reducing the transport cost by dollar transported), or if it is the ``pure'' additive costs (for instance, handling costs) that have reduced over time. As well, we are able to do so for the multiplicative component of trade costs. We also agglomerate the two components in an unified measure of transport costs from which we exclude the composition effects. This allows us to compare how ``pure'' transport costs have changed over time, composition effects excluded, and to compare them to the unfitted ones, reported in Figure \ref{fig:decomp_TC_3d}). Last, for sake of comparison though, we do the same exercise as \citet{hummels2007}.

>>>>

@@

If we share this view with \citet{hummels2007}, our strategy for eliminating composition effects differs from his in two main respects. First, we provide a broader characterization of the time trends in transport costs as our empirical analysis allows for a more flexible estimation of the share between the additive and the ad-valorem components of transport costs. In characterizing the time trend in the ``pure transport costs'', \citet{hummels2007} does not take into account the changes in their additive dimension, attributing this to a change in the composition of the bundle over time (per country-commodity).\footnote{See \citet{hummels2007}, p. 146.} By contrast, our estimation strategy allows for an explicit decomposition of the additive cost component over time/product/country partner.\footnote{The empirical specification of \cite{hummels2007}, as in \cite{hummels_skiba}, assumes a constant share of additive transport costs over time, product and country partner. In \cite{hummels_skiba}, this shows up through the fact that the elasticity of freight costs to prices $\beta$ is constant (with $0<\beta<1$, the lower $\beta$ the larger the additive cost dimension). By contrast, our estimation strategy allows for a varying $\beta$ across time, country partner and product.} By comparing the additive cost component unfitted (total) and fitted (composition effects excluded), we are thus able to characterize if this dimension of the transport cost has fallen due to (for instance) the fact that product quality has increased over time (weight has reduced, hence reducing the transport cost by dollar transported), or if it is the ``pure'' additive costs (for instance, handling costs) that have reduced over time. As well, we are able to do so for the multiplicative component of trade costs. We also agglomerate the two components in an unified measure of transport costs from which we exclude the composition effects. This allows us to compare how ``pure'' transport costs have changed over time, composition effects excluded, and to compare them to the unfitted ones, reported in Figure \ref{fig:decomp_TC_3d}). Last, for sake of comparison though, we do the same exercise as \citet{hummels2007}.
